\subsection{Genetic Algorithms}
Genetic algortithms are a class of metaheiristics ispired by the process of natural selection where the best individuals are the ones with the best fitness/pbjective function value. The general schema of GA is as follows:
\begin{enumerate}
    \item Generate an initial population of individuals.
    \item Evaluate the fitness of each individual.
    \item Repeat until the termination condition is met:
          \begin{enumerate}
              \item Select individuals for reproduction.
              \item Crossover and mutate the selected individuals.
              \item Evaluate the fitness of the new individuals.
              \item Replace the old population with the new population.
          \end{enumerate}
\end{enumerate}

\subsection{Evolution Strategies}
Evolution Strategies are a class of metaheuristics that are similar to genetic algorithms but they are different in the way they handle the mutation and crossover.

\subsection{Particle Swarm Optimization}
Particle Swarm Optimization is a population-based optimization technique that is inspired by the social behavior of a flock of birds searching for food. The algorithms aims at simulation emerginf social behaviours starting from few simple local rules. These rules are:
\begin{itemize}
    \item each position in the environment is associated with a reward
    \item each particle has memory of the best position it visited
    \item each particle gets information from its neighbours
\end{itemize}